Reviewers Comments \& Authors Replies

### 2015-07-20 Report/wsrm_formulation.tex
updated with Nam changes (half cooked)

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers. For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task. We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let 
\begin{IEEEeqnarray}{l}
g({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
\end{IEEEeqnarray}
be a function, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{m}{l,k,n}, \mvec{w}{l,k,n},\beta_{l,k,n}\}} denotes the variables to be identified for an efficient allocation. Note that the function \me{g({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{g({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem in \eqref{eqn-6} is solved iteratively by updating the operating point in each iteration.

For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}  \neqsub
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub
\end{IEEEeqnarray}
and hence \me{g({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notations. In CVX \cite{grant2008cvx}, for example, we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Let \eqn{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\tilde{\mbf{m}}_{l,k,n}, \tilde{\mbf{w}}_{l,k,n},\tilde{\beta}_{l,k,n} \}} be a minimizer from the previous \ac{SCA} iteration. Using the first order Taylor approximation around the operating point \eqn{\tilde{\mbf{u}}_{l,k,n}}, we can approximate \eqref{eqn-6.2} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{l} \label{eqn-8} \IEEEyesnumber
	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{IEEEeqnarray}
}{
\begin{multline}\label{eqn-8}
2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
+ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{multline}
}
In summary, for fixed receivers \me{\tilde{\mbf{w}}_{l,k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}}, the relaxed convex subproblem for finding transmit precoders is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub
\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\tmvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
\end{IEEEeqnarray}

Now, the optimal receivers for fixed transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} are obtained by minimizing \eqref{eqn-6} w.r.t. \me{\mbf{w}_{l,k,n}} as
\begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub
\underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \tmvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
\end{IEEEeqnarray}
Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for an optimal receiver \me{\mbf{w}^{o}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\tmbf{m}}_{j,i,n} {\tmbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\tmbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\tmbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
\end{IEEEeqnarray}
where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex \ac{DC} constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}. The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations. Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective. The dependency is implied by the precoders \me{\mvec{m}{l,k,n}}, which depends on the exponent \me{q}.

It can be seen that the optimal receiver in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \tmvec{m}{j,i,n} \tmvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \tmvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
\end{IEEEeqnarray}
Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance.

\review{The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop denoted by \eqn{i} and the second for the inner \ac{SCA} loop represented by \eqn{j}. Each \ac{AO} loop involves two \ac{SCA} approaches performed until convergence, \textit{i.e.}, at first, the transmit precoders are identified by solving \eqref{eqn-9} iteratively for fixed receivers. In the second step, the receivers are updated with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or using the \ac{MMSE} receiver in \eqref{eqn-10}.

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}. Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{j-1}} \ac{SCA} step. In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{j+1}} \ac{SCA} step is given by \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the optimal receiver obtained by solving \eqref{opt-rx} recursively or by using \eqref{eqn-10} from the \eqn{\ith{i-1}} \ac{AO} step. The \ac{SCA} updates are performed until \eqn{j \rightarrow \infty} or for \eqn{J_{\max}} number of iterations.

Upon convergence of the transmit precoders, the receivers are updated in a similar manner by solving \eqref{eqn-9--1} recursively until \eqn{j \rightarrow \infty} or by using the \ac{MMSE} receiver in \eqref{eqn-10} with the fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step. Once the receivers are obtained, the transmit precoders are again updated by solving \eqref{eqn-9} recursively with the newly found receivers fixed for an operating point. The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations. The overall iterative approach is outlined in Algorithm \ref{algo-1}.

@@

Even though the iterative approach in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to ensure the theoretical convergence of the iterates to a stationary point, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of \eqref{eqn-6.1} due to better convergence properties. The convergence analysis is given in Appendix \ref{sec-3.5}.}
\begin{comment}

>>>>

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. To this end, we resort to the \ac{AO} technique by fixing the linear receivers to solve for the transmit beamformers. For fixed receivers \me{\{\mvec{w}{l,k,n}\}}, \textit{i.e.}, we fix all receivers and not only the one related to \eqn{l,k,n}, the problem now is to find optimal transmit precoders \me{\{\mvec{m}{l,k,n}\}} which is still challenging. By using fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let 
\begin{IEEEeqnarray}{l}
g({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
\end{IEEEeqnarray}
be the r.h.s of \eqref{eqn-6.2}, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{m}{l,k,n}, \mvec{w}{l,k,n},\beta_{l,k,n}\}}. Note that the function \me{g({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. The nonconvex set defined by \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{g({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred to as \ac{SCA} in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem in \eqref{eqn-6} is solved iteratively by updating the operating point in each iteration.

For this purpose, let the real and imaginary components of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}  \neqsub
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub
\end{IEEEeqnarray}
and hence \me{g({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notations. In CVX \cite{grant2008cvx}, for example, we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Let \eqn{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\tilde{\mbf{m}}_{l,k,n}, \tilde{\mbf{w}}_{l,k,n},\tilde{\beta}_{l,k,n} \}} be a minimizer from the previous \ac{SCA} iteration. Using the first order Taylor approximation around the operating point \eqn{\tilde{\mbf{u}}_{l,k,n}}, we can approximate \eqref{eqn-6.2} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{l} \label{eqn-8} \IEEEyesnumber
	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{IEEEeqnarray}
}{
\begin{multline}\label{eqn-8}
2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
+ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{multline}
}
In summary, for fixed receivers \me{\tilde{\mbf{w}}_{l,k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}}, the relaxed convex subproblem for finding transmit precoders is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub
\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\tmvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
\end{IEEEeqnarray}

Now, the optimal receivers for fixed transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} are obtained by minimizing \eqref{eqn-6} w.r.t. \me{\mbf{w}_{l,k,n}} as
\begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub \allowdisplaybreaks
\underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \tmvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
\end{IEEEeqnarray}
Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for an optimal receiver \me{\mbf{w}^{o}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\tmbf{m}}_{j,i,n} {\tmbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\tmbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\tmbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
\end{IEEEeqnarray}
where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}. The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations. Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective. The dependency is implied by the precoders \me{\mvec{m}{l,k,n}}, which depends on the exponent \me{q}.

It can be seen that the optimal receiver in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
\begin{IEEEeqnarray}{rCl} \neqsub
\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \tmvec{m}{j,i,n} \tmvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \tmvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
\end{IEEEeqnarray}
Note that the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, and therefore the \ac{MMSE} receiver in \eqref{eqn-10} can also be used. However, the rate of convergence might be different with the two receivers.

\review{The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop and the second for the inner \ac{SCA} loop. Each \ac{AO} iteration involves two steps, one for finding transmit precoders by solving \eqref{eqn-9} iteratively until convergence for fixed receivers, and the other for updating the receive beamformers with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or by using \eqref{eqn-10}.

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}. Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is given by \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained from the \eqn{\ith{(i-1)}} \ac{AO} step by either solving \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver in \eqref{eqn-10}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} and the constraint set \eqref{eqn-8} with the newly found \me{\mvec{m}{l,k,n}} and \me{\mvec{\beta}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
			$j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

Upon convergence of the transmit precoders, the receivers are updated using the fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step. Once the receive beamformers are obtained, the transmit precoders are again updated by solving \eqref{eqn-9} recursively with the newly found receivers. The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations. The iterative approach is outlined in Algorithm \ref{algo-1}.

@@

Even though the iterative approach in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to provide an analytical convergence proof of the iterates to a stationary point, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of \eqref{eqn-6.1}. The convergence proof for the centralized solutions is provided in Appendix \ref{sec-3.5}.}
\begin{comment}

### 2015-07-20 Response/Response 2/additions.tex
updated with Nam changes (half cooked)

In what follows, the comments are listed, each followed by the corresponding reply from the authors. Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.

>>>>

In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors. The reviewers questions in the revised manuscript are highlighted in blue color and the authors responses are presented in black. Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.

### 2015-07-20 Response/Response 2/document.tex
updated with Nam changes (half cooked)

@@

\vspace{0.5in}
The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality. Based on the comments, we have made several major revisions to the paper, following the suggestions of the reviewers. In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors. The reviewers questions in the revised manuscript are highlighted in blue color and the authors responses are presented in black. Following is the summary of the revision made on the manuscript in accordance with the reviewers comments.
\input{additions}

>>>>

\renewcommand{\thefigure}{\Roman{figure}}
%\renewcommand{\thesubfigure}{\Roman{figure}}
\renewcommand{\theequation}{\roman{equation}}

@@

\vspace{0.5in}
The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality. Based on the comments, we have made several major revisions to the paper, which is summarized below. 
\input{additions}
